Refinement for open automata

### 2021-06-15 2021-Refinement/report.tex
new intro paragraph for properties, might solve some of the issues

>>>>

\Ludo{New}{je suggere un paragraphe du style}
In this section we present a set of  properties that can be desirable for a refinement relation. We reach a point where we state a property that guarantees that the refinement does not create additional deadlock. Unfortunately, in the general case, this property is contradictory with the other ones, this is why we restrict the general composition defined before so that we only consider a composition  to be valid if it does not create deadlocks. With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
